% !TEX root =main.tex






\begin{proof}

Before proving Theorem \ref{theorem::VOPR}, we present Lemma \ref{theorem::evaluation-of-random-poly} and Theorem \ref{theorem:coef-poly-prod} that will be used in the proof of Theorem \ref{theorem::VOPR}. 
\input{vopr-two-theorems}





We refer readers to Appendix \ref{sec::proof-of-poly-union} for the proof of Theorem \ref{theorem:coef-poly-prod}. Next, we  prove the main theorem, i.e., Theorem \ref{theorem::VOPR}, by considering the case where each party is corrupt, in turn. 


% In each case, we invoke the simulator with the corresponding party’s input and output. 

\

\noindent\textbf{Case 1: Corrupt sender.} In the real execution, the sender's view is defined as follows: 


$$ \mathsf{View}_{\st S}^{\st \vopr} \Big((\bm\psi, \bm{\alpha}), \bm\beta\Big)=\{\bm\psi, \bm{\alpha}, r_{\st S},  \bm\beta(z), \bm\theta(z), \mathsf{View}^{\st \ole^{\st +}}_{\st S}, \bot \}$$
%
where $r_{\st S}$ is the outcome of internal random coins of the sender and $\mathsf{View}^{\st \ole^{\st +}}_{\st S}$ refers to the sender's real-model view during the execution of  $\ole^{\st +}$. The simulator $\mathsf{Sim}^{\st \vopr}_{\st S}$, which receives $\bm\psi$ and $\bm \alpha$, works as follows. 
%
\begin{enumerate}
\item generates an empty view. It appends to the view polynomials $(\bm\psi$, $\bm{\alpha})$ and coins $r'_{\st S}$ chosen uniformly at random. 
%
\item computes polynomial $\bm\beta=\bm\beta_{\st 1} \cdot \bm\beta_{\st 2}$, where $\bm\beta_{\st 1}$ is a random polynomial of degree $1$ and $\bm\beta_{\st 2}$ is an arbitrary polynomial of degree $e'-1$. Next,  it constructs polynomial $\bm\theta$ as follows: $\bm\theta=\bm\psi\cdot \bm\beta+\bm \alpha$.

\item picks value $z\stackrel{\st\$}\leftarrow \mathbb{F}_{p}$. Then, it evaluates polynomials $\bm\beta$ and $\bm\theta$  at point $z$. This results in values $\bm\beta_{\st z}$ and $\bm\theta_{\st z}$ respectively. It appends these two values to the view. 
\item extracts the sender-side simulation of $\ole^{\st +}$ from  $\ole^{\st +}$'s simulator. Let $\mathsf{Sim}^{\st \ole^{\st +}}_{\st S}$ be this simulation. Note, the latter simulation is guaranteed to exist, as $\ole^{\st +}$ has been proven secure (in \cite{GhoshN19}). It appends $\mathsf{Sim}^{\st \ole^{\st +}}_{\st S}$ and $\bot$ to its view. 
\end{enumerate}


Now, we are ready to show that the two views are computationally indistinguishable. The sender's inputs are identical in both models, so they have identical distributions. Since the real-model semi-honest adversary samples its randomness according to the protocol's description, the random coins in both models have identical distributions.  Next, we explain why values $\bm\beta(z)$ in the real model and $\bm\beta_{\st z}$ in the ideal model are (computationally) indistinguishable. In the real model, $\bm\beta(z)$ is the evaluation of polynomial $\bm\beta=\bm\beta_{\st 1}\cdot \bm\beta_{\st 2}$ at random point $z$, where $\bm\beta_{\st 1}$ is a random polynomial. We know that $\bm\beta(z)=\bm\beta_{\st 1}(z)\cdot \bm\beta_{\st 2}(z)$, for any (non-zero) $z$.  Moreover, by Lemma \ref{theorem::evaluation-of-random-poly}, we know that $\bm\beta_{\st 1}(z)$ is a uniformly random value. Therefore, $\bm\beta(z)=\bm\beta_{\st 1}(z)\cdot \bm\beta_{\st 2}(z)$ is a uniformly random value as well. In the ideal world, polynomial $\bm\beta$ has the same structure as $\bm\beta$ has (i.e., $\bm\beta=\bm\beta_{\st 1}\cdot \bm\beta_{\st 2}$, where $\bm\beta_{\st 1}$ is a random polynomial). That means $\bm\beta_{\st z}$ is a uniformly random value too. Thus,  $\bm\beta(z)$ and $\bm\beta_{\st z}$ are computationally indistinguishable. Next, we turn our attention to values $\bm\theta(z)$ in the real model and $\bm\theta_{\st z}$ in the ideal model. We know that $\bm\theta(z)$ is a function of $\bm\beta_{\st 1}(z)$, as polynomial $\bm\theta$ has been defined as $\bm\theta=\bm\psi\cdot \bm(\bm\beta_{\st 1}\cdot \bm\beta_{\st 2})+\bm\alpha$. Similarly, $\bm\theta_{\st z}$ is a function of  $\bm\beta_{\st z}$. As we have already discussed,  $\bm\beta(z)$ and $\bm\beta_{\st z}$ are computationally indistinguishable, so are their functions $\bm\theta(z)$ and $\bm\theta_{\st z}$. Moreover, as  $\ole^{\st +}$ has been proven secure,  $\mathsf{View}^{\st \ole^{\st +}}_{\st S}$ and  $\mathsf{Sim}^{\st \ole^{\st +}}_{\st S}$ are computationally indistinguishable. It is also clear that $\bot$ is identical in both models. We conclude that the two views are computationally indistinguishable.


\


\noindent\textbf{Case 2: Corrupt receiver.}  Let $\mathsf{Sim}^{\st\vopr}_{\st R}$ be the simulator, in this case, which uses a subroutine adversary, $\mathcal{A}_{\st R}$. $\mathsf{Sim}^{\st \vopr}_{\st R}$ works as follows. 
%
\begin{enumerate}
%
\item simulates ${\ole^{\st +}}$ and receives $\mathcal{A}_{\st R}$'s input coefficients $b_{\st j}$ for all $j$, $0\leq j \leq e'$, as we are in $f_{\st \ole^{\st +}}$-hybrid model.
%
\item reconstructs polynomial $\bm \beta$, given the above coefficients. 
%
\item simulates the honest sender's inputs as follows. 
%%%%%%%%%
It picks two random polynomials: ${\bm\psi}=\sum\limits^{\st e}_{\st i=0}{g}_{\st i}\cdot x^{\st i}$ and  ${\bm\alpha}=\sum\limits^{\st e+e'}_{\st j=0}{a}_{\st j}\cdot x^{\st j}$, such that ${g}_{\st i}\stackrel{\st \$}\leftarrow \mathbb{F}_{\st p}$ and  every $a_{\st j}$ has the  form: $a_{\st j}=\sum\limits^{\substack{\st k=e'\\ \st t=e}}_{\st t,k=0} a_{\st t,k}$,  where $t+k=j$ and $a_{\st t,k}\stackrel{\st \$}\leftarrow \mathbb{F}_{\st p}$. 
%%%%%%%
\item sends to ${\ole^{\st +}}$'s functionality values $g_{\st i}$ and $a_{\st i,j}$ and receives   $c_{\st i,j}$ from this functionality (for all $i,j$).
%
\item sends all ${c}_{\st i,j}$ to TTP and receives polynomial ${\bm\theta}$. 
%
\item picks a random value $ z$ from $\mathbb{F}_{\st p}$. Then, it computes $ \psi_{\st  z} = {\bm\psi}(  z)$ and $\alpha_{\st  z}= {\bm\alpha}(z)$. 
%
\item sends $ z$ and all ${c}_{\st i,j}$ to $\mathcal{A}_{\st R}$ which sends back $\theta_{ z}$ and $\beta_{\st z}$ to the simulator. 
%
\item sends  $ \psi_{\st  z}$ and $\alpha_{\st z}$ to $\mathcal{A}_{\st R}$. 
%
\item checks if the following relation hold:
%
\begin{equation}\label{equ::beta}
 \beta_{\st \bar z}={\bm\beta}( z) \hspace{6mm} \wedge \hspace{6mm} \theta_{\st  z}={\bm\theta}( z) \hspace{6mm}\wedge\hspace{6mm} {\bm\theta}( z)=  \psi_{\st  z}\cdot \beta_{\st  z}+\alpha_{\st  z}
 \end{equation}
 %
% \begin{equation}\label{equ::theta}
% \bar\theta_{\st \bar z}=\bar{\bm\theta}(\bar z) 
% \end{equation}
% %
%\begin{equation}\label{equ::theta-equals=psi}
%\bar{\bm\theta}(\bar z)= \bar \psi_{\st \bar z}\cdot \bar\beta_{\st \bar z}+\bar\alpha_{\st  \bar z}
%  \end{equation}
%%
% \begin{equation}\label{equ::theta-evl-equals=psi}
% \bar\theta_{\st \bar z}= \bar \psi_{\st \bar z}\cdot \bar\beta_{\st \bar z}+\bar\alpha_{\st  \bar z}
 %\end{equation}
%





%%%%%%%%%%%%%%%


%
% $\bar{\bm\theta}(\bar z) =\bar\theta_{\st \bar z} = \bar \psi_{\st \bar z}\cdot \bar\beta_{\st \bar z}+\bar\alpha_{\st  \bar z}$. 
 %
 If Relation \ref{equ::beta} does not hold, it aborts (i.e., sends abort signal $\Lambda$ to the sender) and still proceeds to the next step. 
 
 \item outputs whatever $\mathcal{A}_{\st R}$ outputs. 
%
\end{enumerate}

We first focus on the adversary's output. Both values of $z$ in the real and ideal models have been picked uniformly at random from $\mathbb{F}_{\st p}$; therefore, they have identical distributions. In the real model, values  $\psi_{\st z}$ and $\alpha_{\st z}$ are the result of the evaluations of two random polynomials at (random) point $z$. In the ideal model, values $\psi_{\st  z}$ and $\alpha_{\st z}$ are also the result of the evaluations of two random polynomials (i.e., ${\bm\psi}$ and ${\bm\alpha}$) at point $ z$.  By Lemma \ref{theorem::evaluation-of-random-poly}, we know that the evaluation of a random polynomial at an arbitrary value  
 yields a uniformly random value in $\mathbb{F}_{\st p}$. Therefore, the distribution of pair $(\psi_{\st z}, \alpha_{\st z})$ in the real model is identical to that of pair $( \psi_{\st  z}, \alpha_{\st  z})$ in the ideal model. Moreover, the final result (i.e., values ${c}_{\st i,j}$) in the real model has the same distribution as the final result (i.e., values ${c}_{\st i,j}$)  in the ideal model, as they are the outputs of the ideal calls to $f_{\st \ole^{\st +}}$, as we are in the $f_{\st \ole^{\st +}}$-hybrid model. 

Next, we turn our attention to the sender's output. We will show that the output distributions of the honest sender in the ideal and real models are statistically close. 
%
%Note that the messages distributions the sender receive from the ideal call to $f_{\st \text{OLE}^{\st +}}$ are identical in both models. 
%
Our focus will be on the probability that it aborts in each model, as it does not receive any other output. In the ideal model, $\mathsf{Sim}^{\st \vopr}_{\st R}$ is given the honestly generated result polynomial ${\bm \theta}$ (computed by TTP) and the adversary's input polynomial ${\bm \beta}$. $\mathsf{Sim}^{\st \vopr}_{\st R}$ aborts with a probability of 1 if Relation \ref{equ::beta} does not hold. However, in the real model, the honest sender (in addition to its inputs) is given only $\beta_{\st  z}$ and $\theta_{\st  z}$ and is not given polynomials ${\bm\beta}$ and  ${\bm\theta}$; it wants to check if the following equation holds, $\theta_{\st z} =  \psi_{\st z}\cdot  \beta_{\st z}+ \alpha_{\st z}$. Note, polynomial $\bm\theta=\bm\psi\cdot \bm\beta+\bm\alpha$ (resulted from ${c}_{\st i,j}$) is well-structured, as it satisfies the following three conditions, regardless of the adversary's input $\bm\beta$ to $\ole^{\st +}$, (i) $deg(\bm\theta)=Max \Big(deg(\bm\beta)+deg(\bm\psi), deg(\bm\alpha) \Big)$, as $\mathbb{F}_{\st p}[X]$ is an integral domain and ($\bm\psi,\bm\alpha$) are random polynomials, (ii)  the roots of the product polynomial $\bm\nu=\bm\psi\cdot \bm\beta$ contains exactly both polynomials' roots, by Theorem \ref{theorem:coef-poly-prod}, and (iii)  the roots of $\bm\nu+\bm\alpha$ is the intersection of the roots of $\bm\nu$ and $\bm\alpha$, as shown in \cite{DBLP:conf/crypto/KissnerS05}. Furthermore, polynomial $\bm \theta$ reveals no information (about  $\bm \psi$ and $\bm\alpha$ except their degrees) to the adversary and the pair $(\psi_{\st z}, \alpha_{\st z})$ is given to the adversary after it sends the pair $(\theta_{\st z}, \beta_{\st z})$ to the sender. 
%
There are exactly four cases where pair $(\theta_{\st z}, \beta_{\st z})$ can be constructed by the real-model adversary. Below, we state each case and the probability that the adversary is detected in that case during the verification, i.e., $\theta_{\st z}\stackrel{\st ?}=\psi{\st z}\cdot \beta_{\st z}+\alpha_{\st z}$. 
%
\begin{enumerate}
%
\item $\theta_{\st z}= \bm\theta(z) \wedge  \beta_{\st  z}={\bm\beta}( z)$. This is a trivial non-interesting case, as the adversary has behaved honestly, so it can always pass the verification. %, i.e., $\theta_{\st z}\stackrel{\st ?}=\psi{\st z}\cdot \beta_{\st z}+\alpha_{\st z}$.
%
\item $\theta_{\st z}\neq \bm\theta(z) \wedge  \beta_{\st  z}={\bm\beta}( z)$. In this case, the adversary is detected with a probability of 1. 
%
\item $\theta_{\st z}= \bm\theta(z) \wedge  \beta_{\st  z}\neq {\bm\beta}( z)$.  In this case, the adversary is also detected with a probability of 1.
%
\item $\theta_{\st z}\neq \bm\theta(z) \wedge  \beta_{\st  z} \neq {\bm\beta}( z)$. In this case, the adversary is detected with an overwhelming probability, i.e., $1-\frac{1}{2^{\st 2\lambda}}$. 
%
\end{enumerate}

As we illustrated above, in the real model, the lowest probability that the honest sender would abort in case of adversarial behaviour is $1-\frac{1}{2^{\st 2\lambda}}$. Thus, the honest sender's output distributions in the ideal and real models are statistically close, i.e., $1$ \text{vs} $1-\frac{1}{2^{\st 2\lambda}}$. 

We conclude that the distribution of the joint outputs of the honest sender and adversary in the real and ideal models are computationally indistinguishable. 
  \hfill\(\Box\)\end{proof}
  
  
  
  
  
  
  
  
  
  
  
  