% !TEX root =main.tex


%%%%%%%%%%%%%%%%%
\section{Further Discussion on  \withFai}\label{sec::Discussion-justitia}


\subsection{Input and Output Privacy}

Intuitively, all parties locally blind/encrypt all (set element related) messages before they send them the smart contract \scf. Moreover, the resultant polynomial that \scf computes is in a blinded form and it reveals only the intersection of the sets after it is unblinded (as discussed in Section \ref{sec::poly-rep}, on page \pageref{sec::poly-rep}).


Hence, (i) no party (including the protocol's participants) can learn other parties input set elements and (ii) the non-participants of the protocol cannot learn anything about the protocol's output, not even the intersection cardinality. 


\subsection{Strawman Approaches}


\subsubsection{Relying on a Server-aide PSI.} One may be tempted to replace $\withFai$ with a scheme in which all clients send their encrypted sets to a server (potentially semi-honest and plays \aud's role) which computes the result in a privacy-preserving manner.  We highlight that the main difference is that in this (hypothetical) scheme the server is \emph{always involved};  whereas, in our protocol, \aud remains offline as long as the clients behave honestly and it is invoked only when the contract detects misbehaviours.  


\subsubsection{Charging the Buyer a Flat Fee.}

One might wish to incorporate a straightforward payment mechanism into an existing multi-party PSI such that a buyer is always required to pay a fixed amount, which could depend on factors such as the total number of clients and the minimum size of the sets. However, this approach presents challenges, because:

\begin{enumerate}
\item it compels the buyer to make payments even if certain malicious clients misbehave during the protocol execution and compromise the accuracy of the results. This situation could enable malicious clients to gain access to the result at the buyer's expense without allowing the buyer to obtain the correct result. Unfortunately, there is no fair multi-party PSI in the existing literature that guarantees either all parties learn the correct result or none of them do. 

\item it compels the buyer to make payments regardless of the precise size of the intersection. If the buyer ends up paying more than the amount it would have paid for the exact cardinality of the intersection, it might become discouraged from participating in the protocol altogether. Conversely, if the buyer has to pay less than what it would have paid for the size of the intersection, it may discourage other clients from participating in the protocol.

\end{enumerate}



\input{error-prob}


 
\input{Justitia-challenges}

\input{zeta}

\input{Concrete-parameters}
